Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-13 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 Both the Poisson Scan Statistic proposed by Kulldorff, the Global and the Local Moran's I were already used before in studies about spatial and Spatio-temporal characteristics of Sars-CoV-2, whereas the Scan Statistic for instance was used once in studies about the Spatio-temporal behavior of Covid-19 in the state of Sergipe in Brazil, while both the Global Moran's I and the LISA were used in Chinese studies regarding the spatial characteristics of the pandemic in China, in this paper these methods showed themselves to be useful when there is a need to study spatial and Spatio-temporal characteristics of a virus.

@@

>>>>

 Both the Poisson Scan Statistic proposed by Kulldorff, the Global and the Local Moran's I were already used before in studies about spatial and Spatio-temporal characteristics of Sars-CoV-2, whereas the Scan Statistic for instance was used once in studies about the Spatio-temporal behavior of Covid-19 in the state of Sergipe in Brazil $\!\!^1\!^0$, while both the Global Moran's I and the LISA were used in Chinese studies regarding the spatial characteristics of the pandemic in China  $\!\!^1\!^1$, in this paper these methods showed themselves to be useful when there is a need to study spatial and Spatio-temporal characteristics of a virus.

@@

[10] - ANDRADE, Lucas Almeida et al. Surveillance of the first cases of COVID-19 in Sergipe using a prospective spatiotemporal analysis: the spatial dispersion and its public health implications. Rev. Soc. Bras. Med. Trop. [online]. 2020, vol.53 [cited  2021-01-13], e20200287. Available from: <http://www.scielo.br/scielo.php?script=sci_arttext&pid=S0037-86822020000100641&lng=en&nrm=iso>.  Epub June 01, 2020. ISSN 1678-9849.  https://doi.org/10.1590/0037-8682-0287-2020

[11] - Dayun Kang, Hyunho Choi, Jong-Hun Kim, Jungsoon Choi,
Spatial epidemic dynamics of the COVID-19 outbreak in China,
International Journal of Infectious Diseases, Volume 94, 2020, Pages 96-102, ISSN 1201-9712, Available at: <https://www.sciencedirect.com/science/article/pii/S1201971220302095>. https://doi.org/10.1016/j.ijid.2020.03.076.
